---
title: "Supporting Information"
editor_options:
  chunk_output_type: console
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

MacDonald, A. J., P. A. Smith, C. A. Friis, J. E. Lyons, Y. Aubry, and E. Nol. 2021. Stopover Ecology of Red Knots in Southwestern James Bay During Southbound Migration. Journal of Wildlife Management.

## JAGS code for integrated analyses

All JAGS and R code for the analyses in this paper is available in the paper's GitHub repository: <https://github.com/ajmacdonald3/REKN-passage-population> (last updated 28 Feb 2021).

JAGS code adapted from Lyons et al. (2016), Lyons et al. (2018), and Kéry and Schaub (2012).

### 2017 model

```{r, eval = FALSE}

    model {
    # Priors and constraints
    for (i in 1:M){
    for (t in 1:(n.occasions-1)){
    phi[i,t] <- phi_t[t]
    } #t
    for (t in 1:n.occasions){
    p[i,t] <- psight[t]
    } #t
    } #i
    
    # Persistence
    
    for (t in 1:(n.occasions-1)) {
    logit(phi_t[t]) <- mu_phi + epsilon_phi[t]
    epsilon_phi[t] ~ dnorm(0, tau_phi)
    }
    
    mean.phi ~ dunif(0, 1)                 # prior for mean survival
    mu_phi <- log(mean.phi / (1-mean.phi)) # logit transformation
    sigma_phi ~ dunif(0, 5)                # prior for standard deviation
    tau_phi <- pow(sigma_phi, -2)
    sigma_phi2 <- pow(sigma_phi, 2)        # temporal variance
    sigma_phi2.real <- sigma_phi2 * pow(mean.phi, 2) * pow((1-mean.phi), 2) # Temporal
    #variance on real scale
    
    # Resight
    
    for (t in 1:n.occasions) {
    logit(psight[t]) <- mu_p + epsilon_p[t]
    epsilon_p[t] ~ dnorm(0, tau_p)
    }
    
    mean.p ~ dunif(0, 1)             # prior for mean survival
    mu_p <- log(mean.p / (1-mean.p)) # logit transformation
    sigma_p ~ dunif(0, 5)           # prior for standard deviation
    tau_p <- pow(sigma_p, -2)
    sigma_p2 <- pow(sigma_p, 2)      # temporal variance
    sigma_p2.real <- sigma_p2 * pow(mean.p, 2) * pow((1-mean.p), 2) # Temporal
    #variance on real scale

    # Prior for inclusion probability

    psi ~ dunif(0, 1)              
    
    # Dirichlet prior for entry probabilities
    for (t in 1:(n.occasions-1)){
    beta[t] ~ dgamma(1, 1)
    b[t] <- beta[t] / sum(beta[1:(n.occasions-1)])
    }
    
    b[14] <- 0 # set last period to 0
    
    # Convert entry probs to conditional entry probs
    nu[1] <- b[1]
    for (t in 2:n.occasions){
    nu[t] <- b[t] / (1-sum(b[1:(t-1)]))
    } #t
    
    # Likelihood
    for (i in 1:M){
    # First occasion
    # State process
    w[i] ~ dbern(psi)                  # Draw latent inclusion
    z[i,1] ~ dbern(nu[1])
    # Observation process
    mu1[i] <- z[i,1] * p[i,1] * w[i]
    y[i,1] ~ dbern(mu1[i])
    
    # Subsequent occasions
    for (t in 2:n.occasions){
    # State process
    q[i,t-1] <- 1-z[i,t-1]
    mu2[i,t] <- phi[i,t-1] * z[i,t-1] + nu[t] * prod(q[i,1:(t-1)]) 
    z[i,t] ~ dbern(mu2[i,t])
    # Observation process
    mu3[i,t] <- z[i,t] * p[i,t] * w[i]
    y[i,t] ~ dbern(mu3[i,t])
    } #t
    } #i 
    
    # ------------- flag scans ---------------------------------  

    # GLMM for scan samples
    
    # Priors
    
    alpha ~ dnorm(0,0.001)
    
    for (i in 1:n.per) {
    delta[i] ~ dnorm(0, tau.per)
    }
    
    tau.per <- pow(sigma.per, -2)
    
    sigma.per ~ dunif(0,10)
    
    # Likelihood
    
    for (i in 1:n) {
    m[i] ~ dbin(lp[i],K[i])
    
    logit(lp[i]) <- alpha + delta[ per[i] ]
    }
    
    for (i in 1:n.per) {
    pflag[i] <- exp(alpha + delta[i])/(1 + exp(alpha + delta[i]))
    }
    
    meanpflag <- exp(alpha)/(1 + exp(alpha))
    
    # ------------- end : flag scans ---------------------------------
    
    # ------------- age scans ---------------------------------  
    # GLM for age scans
    
    # Priors
    
    for (i in 1:n.per) {
    beta.rper[i] ~ dnorm(0, 0.001)
    }
    
    # Likelihood
    
    for (i in 1:n2) {
    a[i] ~ dbin(pad[i],Tot[i]) # Distribution for random part
    logit(pad[i]) <- beta.rper[ rper[i] ] # Link function and linear predictor
    }
    
    for (j in 1:n.per) {
    padult[j] <- 1/(1 + exp(-beta.rper[j])) # convert logit to prob/proportion
    }
    
    meanpadult <- mean(padult[])
    
    # ------------- end : age scans ---------------------------------
    
    # Calculate derived population parameters
    for (i in 1:M){
    for (t in 1:n.occasions){
    u[i,t] <- z[i,t]*w[i]     # Deflated latent state (u)
    }
    }
    for (i in 1:M){
    recruit[i,1] <- u[i,1]
    for (t in 2:n.occasions){
    recruit[i,t] <- (1-u[i,t-1]) * u[i,t]
    } #t
    } #i
    
    for (t in 1:n.occasions){
    Nflag[t] <- sum(u[1:M,t])                         # Number of flagged birds
    Nstopadult[t]   <- sum( u[1:M,t] )/pflag[t]
    Nstop_t[t] <- sum(( u[1:M,t] )/pflag[t])/padult[t]
    Bflag[t] <- sum(recruit[1:M,t])                   # Number of flagged entries
    Bstopadult[t]  <- sum(recruit[1:M,t])/pflag[t]
    Bstop_t[t] <- (sum((recruit[1:M,t]))/pflag[t])/padult[t]
    } #t
    
    for (i in 1:M){
    Nind[i] <- sum(u[i,1:n.occasions])
    Nalive[i] <- 1-equals(Nind[i], 0)
    } #i
    
    Nsuperflag <- sum(Nalive[])         # Superpopulation size
    Nsuperstopadult <- sum(Bstopadult[])
    Nsuperstop_Bt <- sum(Bstop_t[])
    
    # ------------------- Stopover duration -----------------------------------
    for (i in 1:n.ch) {
    zstop[i] <- sum(u[i,1:n.occasions])*3
    }
    zes.days <- mean(zstop[])
    # ------------------- end : Stopover duration ---------------------------------
    
    }

```

### 2018 model

```{r, eval = FALSE}

    model {
    # Priors and constraints
    for (i in 1:M){
    for (t in 1:(n.occasions-1)){
    phi[i,t] <- phi_t[t]
    } #t
    for (t in 1:n.occasions){
    p[i,t] <- psight[t]
    } #t
    } #i
    
    # Persistence
    
    for (t in 1:(n.occasions-1)) {
    logit(phi_t[t]) <- mu_phi + epsilon_phi[t]
    epsilon_phi[t] ~ dnorm(0, tau_phi)
    }
    
    mean.phi ~ dunif(0, 1)                 # prior for mean survival
    mu_phi <- log(mean.phi / (1-mean.phi)) # logit transformation
    sigma_phi ~ dunif(0, 5)                # prior for standard deviation
    tau_phi <- pow(sigma_phi, -2)
    sigma_phi2 <- pow(sigma_phi, 2)        # temporal variance
    sigma_phi2.real <- sigma_phi2 * pow(mean.phi, 2) * pow((1-mean.phi), 2) # Temporal
    #variance on real scale
    
    # Resight
    
    for (t in 1:n.occasions) {
    logit(psight[t]) <- mu_p + epsilon_p[t]
    epsilon_p[t] ~ dnorm(0, tau_p)
    }
    
    mean.p ~ dunif(0, 1)             # prior for mean survival
    mu_p <- log(mean.p / (1-mean.p)) # logit transformation
    sigma_p ~ dunif(0, 5)           # prior for standard deviation
    tau_p <- pow(sigma_p, -2)
    sigma_p2 <- pow(sigma_p, 2)      # temporal variance
    sigma_p2.real <- sigma_p2 * pow(mean.p, 2) * pow((1-mean.p), 2) # Temporal
    #variance on real scale

    # Prior for inclusion probability

    psi ~ dunif(0, 1)              
    
    # Dirichlet prior for entry probabilities
    for (t in 1:(n.occasions-2)){
    beta[t] ~ dgamma(1, 1)
    b[t] <- beta[t] / sum(beta[1:(n.occasions-2)])
    }
    
    for (t in (n.occasions-1):n.occasions){
    b[t] <- 0 # set last two periods to 0
    }
    
    # Convert entry probs to conditional entry probs
    nu[1] <- b[1]
    for (t in 2:n.occasions){
    nu[t] <- b[t] / (1-sum(b[1:(t-1)]))
    } #t
    
    # Likelihood
    for (i in 1:M){
    # First occasion
    # State process
    w[i] ~ dbern(psi)                  # Draw latent inclusion
    z[i,1] ~ dbern(nu[1])
    # Observation process
    mu1[i] <- z[i,1] * p[i,1] * w[i]
    y[i,1] ~ dbern(mu1[i])
    
    # Subsequent occasions
    for (t in 2:n.occasions){
    # State process
    q[i,t-1] <- 1-z[i,t-1]
    mu2[i,t] <- phi[i,t-1] * z[i,t-1] + nu[t] * prod(q[i,1:(t-1)]) 
    z[i,t] ~ dbern(mu2[i,t])
    # Observation process
    mu3[i,t] <- z[i,t] * p[i,t] * w[i]
    y[i,t] ~ dbern(mu3[i,t])
    } #t
    } #i 
    
    # ------------- flag scans ---------------------------------  
    
    # GLMM for scan samples
    
    # Priors
    
    alpha ~ dnorm(0,0.001)
    
    for (i in 1:n.per) {
    delta[i] ~ dnorm(0, tau.per)
    }
    
    tau.per <- pow(sigma.per, -2)
    
    sigma.per ~ dunif(0,10)
    
    # Likelihood
    
    for (i in 1:n) {
    m[i] ~ dbin(lp[i],K[i])
    
    logit(lp[i]) <- alpha + delta[ per[i] ]
    }
    
    for (i in 1:n.per) {
    pflag[i] <- exp(alpha + delta[i])/(1 + exp(alpha + delta[i]))
    }
    
    meanpflag <- exp(alpha)/(1 + exp(alpha))
    
    # ------------- end : flag scans ---------------------------------
    
    # ------------- age scans ---------------------------------  
    # GLM for age scans
    
    # Priors
    
    for (i in 1:n.per) {
    beta.rper[i] ~ dnorm(0, 0.001)
    }
    
    # Likelihood
    
    for (i in 1:n2) {
    a[i] ~ dbin(pad[i],Tot[i]) # Distribution for random part
    logit(pad[i]) <- beta.rper[ rper[i] ] # Link function and linear predictor
    }
    
    for (j in 1:n.per) {
    padult[j] <- 1/(1 + exp(-beta.rper[j])) # convert logit to prob/proportion
    }
    
    meanpadult <- mean(padult[])
    
    # ------------- end : age scans ---------------------------------
    
    # Calculate derived population parameters
    for (i in 1:M){
    for (t in 1:n.occasions){
    u[i,t] <- z[i,t]*w[i]     # Deflated latent state (u)
    }
    }
    for (i in 1:M){
    recruit[i,1] <- u[i,1]
    for (t in 2:n.occasions){
    recruit[i,t] <- (1-u[i,t-1]) * u[i,t]
    } #t
    } #i
    
    for (t in 1:n.occasions){
    Nflag[t] <- sum(u[1:M,t])                         # Number of flagged birds
    Nstopadult[t]   <- sum( u[1:M,t] )/pflag[t]
    Nstop_t[t] <- sum(( u[1:M,t] )/pflag[t])/padult[t]
    Bflag[t] <- sum(recruit[1:M,t])                   # Number of flagged entries
    Bstopadult[t]  <- sum(recruit[1:M,t])/pflag[t]
    Bstop_t[t] <- (sum((recruit[1:M,t]))/pflag[t])/padult[t]
    } #t
    
    for (i in 1:M){
    Nind[i] <- sum(u[i,1:n.occasions])
    Nalive[i] <- 1-equals(Nind[i], 0)
    } #i
    
    Nsuperflag <- sum(Nalive[])         # Superpopulation size
    Nsuperstopadult <- sum(Bstopadult[])
    Nsuperstop_Bt <- sum(Bstop_t[])
    
    # ------------------- Stopover duration -----------------------------------
    for (i in 1:n.ch) {
    zstop[i] <- sum(u[i,1:n.occasions])*3
    }
    zes.days <- mean(zstop[])
    # ------------------- end : Stopover duration ---------------------------------
    
    }

```

**Literature Cited**



Kéry, M., and M. Schaub. 2012. Bayesian population analysis using WinBUGS: a hierarchical perspective. Academic Press, Waltham, Massachusetts, USA.

Lyons, J. E., W. L. Kendall, J. A. Royle, S. J. Converse, B. A. Andres, and J. B. Buchanan. 2016. Population size and stopover duration estimation using mark-resight data and Bayesian analysis of a superpopulation model. Biometrics 72:262–271. 

Lyons, J. E., B. Winn, T. Keyes, and K. S. Kalasz. 2018. Post-breeding migration and connectivity of Red Knots in the Western Atlantic. Journal of Wildlife Management 82:383–396.

R Core Team. 2020. R: A language and environment for statistical computing. R Foundation
for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.